The Ontological Modal Collapse \\ as a Collapse of the Square of Opposition

### 2014-09-10 Papers/Universalis/ModalCollapse.tex
Add paragraph about weakness in the integration

Ongoing and future work includes the study of modal collapse in
other variants of the ontological argument (e.g.~\cite{bjordal99,fuhrmann05:_exist_notwen}).

>>>>

Ongoing and future work includes the computer-assisted 
study of the modal collapse in
other variants of the ontological argument (e.g.~\cite{bjordal99,fuhrmann05:_exist_notwen}). Furthermore, our experiments in Isabelle revealed a weakness of the current integration of the HOL-ATPs LEO-II and Satallax via Sledgehammer: most of the problems in our study solved by the two HOL-ATPs were still too hard to be reconstructed and verified by Isabelle's internal prover Metis. This points to relevant future work regarding the integration of HOL-ATPs in Isabelle.
